Fusion of Mass Spectrometry and Raman Spectroscopy Data

### 2024-05-10 dev/dev_paracetamol.Rmd
Initiated StatisticEngine
Added extra funcs in StatisticEngine

mSpec <- ms$get_spectra()
mSpec <- mSpec[order(mSpec$replicate), ]
mmSpec <- matrix(mSpec$intensity, nrow = length(unique(mSpec$replicate)), ncol = length(unique(mSpec$bins)), byrow = TRUE, dimnames = list(unique(mSpec$replicate), unique(mSpec$bins)))

@@

@@

```{r}
# rownames(fusedMat)
main_set <- fusedMat[c(14:15, 18), ]
test_set <- fusedMat[c(1:13, 16:17, 19:30), ]

m3 = pca(main_set, 2, center = FALSE, scale = FALSE, info = "Unsupervised PCA model", alpha = 1E-1, gamma = 1E-2)

@@

@@

plotResiduals(m3, 
  res = list("train" = m3$res$cal, "new" = res),
  norm = TRUE, show.labels = TRUE,
  lim.col = c("red", "orange"), lim.lwd = c(2, 2), lim.lty = c(1, 2)
)

print(c)
```

>>>>

mSpec <- ms2$get_spectra()
mSpec <- mSpec[order(mSpec$replicate), ]
mmSpec <- matrix(mSpec$intensity, nrow = length(unique(mSpec$replicate)), ncol = length(unique(mSpec$bins)), byrow = TRUE, dimnames = list(unique(mSpec$replicate), unique(mSpec$bins)))

@@

# stat <- StatisticEngine$new(data = fusedMat)
# stat$make_pca_model(Settings_make_pca_model_mdatools(center = TRUE, ncomp = 3))
# stat$plot_model_scores()
# stat$plot_model_loadings()
# stat$plot_model_residuals()
# subset matrix for 1 row but keep matrix not vector

@@

```{r}
library(mdatools)
# rownames(fusedMat)
main_set <- fusedMat[c(14:15, 18), ]
test_set <- fusedMat[c(1:13, 16:17, 19:30), ]

m3 = pca(main_set, 3, center = FALSE, scale = FALSE, info = "Unsupervised PCA model", alpha = 1E-1, gamma = 1E-2)

@@

plot(res)

@@

plotResiduals(m3,
  ncomp = 2,
  res = list("train" = m3$res$cal, "new" = res),
  norm = TRUE, show.labels = TRUE,
  lim.col = c("red", "orange"), lim.lwd = c(2, 2), lim.lty = c(1, 2)
)

plotResiduals(res, show.plot = FALSE, norm = TRUE)

print(c)

is(m3$res$cal, "ldecomp")

stat <- StatisticEngine$new(data = main_set)
stat$make_pca_model(Settings_make_pca_model_mdatools(center = FALSE, ncomp = 3, alpha = 1E-1, gamma = 1E-2))
stat$predict(test_set)

stat$plot_predicted_distances()

```
